Impact of interaction network structure on community-level plant reproductive success

### 2018-11-19 paper.Rmd
comments by nacho

---
title: "Paper"
author: "Ainhoa Magrach"
date: "6 November 2018"
output: html_document
---

---
title: Impact of interaction network structure on community-level plant reproductive success 
author: "Magrach, A & Bartomeus, I"
date: "6 November 2018"
output: html_document
---

@@

#setwd("~/Dropbox/Beefun/Beefun/functioning")
setwd("C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning")

@@

#Fruit_Yes +  Fruit_Preyed + Fruit_Dispersed) / (Fruit_Yes + Fruit_No +Fruit_Preyed + Fruit_Dispersed) #Nacho this equation is wrong in your metadata!

@@

f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed)

s2<-subset(s, Notes %nin% wordList)
s2$tot.seedset

@@

f.agg2<-na.omit(f.agg)
#cor(f.agg2[,c(5:13, 15:24)])

@@

@@

pl1

@@

mp2<-subset(mp, mp$mean.fruitset!="NA")
mp2$class[mp2$mean.fruitset>0.5]<-"high"
mp2$class[mp2$mean.fruitset<0.5]<-"low"

# How many native and introduced species?
mp2 <- mp2[order(mp2$class, decreasing = TRUE),]
class_f <- table(mp2$class)

# NMDS
example_NMDS <- metaMDS(vegdist(mp2[,paste0("m",1:46)], method = "bray"), k=2, distance = "bray", trymax = 100)
mds.fig <- ordiplot(example_NMDS, type = "none")
colors=c(rep("darkorange2",class_f["low"]),rep("purple",class_f["high"]))
treat <- mp2$class
for(i in unique(treat)) {
  ordihull(example_NMDS$point[grep(i,treat),],draw="polygon",
           groups=treat[treat==i],col=colors[grep(i,treat)],label=F) } 
with(mp2, legend("topright", legend = unique(mp2$class), bty = "n",
                col = unique(colors), pch = 21, pt.bg = unique(colors)))
points(mds.fig, "sites", pch = 19, col = "darkorange3", select = mp2$class == 
         "low")
points(mds.fig, "sites", pch = 19, col = "purple", select = mp2$class == 
         "high")

@@

#permanova

adonis(mp2[,3:48]~ class, data=mp2, method = "bray")

#no significant differences

>>>>

---
title: Impact of interaction network structure on community-level plant reproductive success 
author: "Magrach, A, Molina, C, Bartomeus, I"
date: "6 November 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

#setwd("~/Dropbox/Beefun/Beefun/functioning")
#setwd("C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning") #use rstudio projects and avoid wd issues.
#I am uploading a Rproj. just cleick there to open it the next time.

@@

#Fruit_Yes +  Fruit_Preyed + Fruit_Dispersed) / (Fruit_Yes + Fruit_No + Fruit_Preyed + Fruit_Dispersed) #Nacho this equation is wrong in your metadata!

@@

f2$tot.fruitset<-(f2$Fruit_Yes +  f2$Fruit_preyed + f2$Fruit_dispersed)/(f2$Fruit_Yes +f2$Fruit_No + f2$Fruit_preyed + f2$Fruit_dispersed) #why not use a binomial response and use both the numerator and the denominator? mmm... this will bias the estimates for plants producing larger number of seeds.

s2<-subset(s, Notes %nin% wordList)
s2$tot.seedset #this variable do not exists

@@

f.agg2<-na.omit(f.agg) #you are ommiting here also NA's on SE, which is consevartive.
#cor(f.agg2[,c(5:13, 15:24)])

@@

m1.fr3<-glmmTMB(mean.fruitset ~ nodf.song + functional.comp.poll +   (1|Plant.sp), family="gaussian", data=f.agg2)
summary(m1.fr3)

@@

pl1 #This suggests random slopes...

@@

mp2<-subset(mp, mp$mean.fruitset!="NA")
mp2$class[mp2$mean.fruitset<0.75]<-"mid"
mp2$class[mp2$mean.fruitset<0.5]<-"low"
mp2$class[mp2$mean.fruitset>0.75]<-"high"

# How many native and introduced species?
mp2 <- mp2[order(mp2$class, decreasing = TRUE),]
class_f <- table(mp2$class)
#lots of empty positions. why?

#test mcount(M = m, six_node = TRUE, normalise = TRUE)
test <- mcount(M = webs[[1]], six_node = FALSE, normalise = TRUE)
sum(test$nodes) #74 positions

#see one position model
plot(mp2$mean.fruitset ~ mp2$m2)

pca <- prcomp(mp2[,3:48]) #there are two cases that break everything...
biplot(pca)
summary(pca)

#Notes, before doing the NMDS wes should remove imposible positions (e.g. 1,3,5,7,... for pollinators.)
# NMDS
example_NMDS <- metaMDS(vegdist(mp2[,paste0("m",1:46)], method = "euclidian"), k=2, distance = "bray", trymax = 100)
mds.fig <- ordiplot(example_NMDS, type = "none")
colors=c(rep("yellow",class_f["low"]), rep("darkorange2",class_f["mid"]),rep("purple",class_f["high"]))
treat <- mp2$class
for(i in unique(treat)) {
  ordihull(example_NMDS$point[grep(i,treat),],draw="polygon",
           groups=treat[treat==i],col=colors[grep(i,treat)],label=F) } 
with(mp2, legend("topright", legend = unique(mp2$class), bty = "n",
                col = unique(colors), pch = 21, pt.bg = unique(colors)))
points(mds.fig, "sites", pch = 19, col = "darkorange3", select = mp2$class == 
         "low")
points(mds.fig, "sites", pch = 19, col = "yellow", select = mp2$class == 
         "mid")
points(mds.fig, "sites", pch = 19, col = "purple", select = mp2$class == 
         "high")

@@

#permanova... we need to control for the web, right?

adonis(mp2[,3:48]~ mean.fruitset, data=mp2, method = "euclidian", strata = mp2$web)
adonis(mp2[,3:48]~ class, data=mp2, method = "bray")

#no significant differences at all.
